\vspace*{-8mm}\textbf{\textsc{Novelty Detection for Semantic Place Categorization}}

### 2011-07-04 thesis/background.tex
Added summary on end of background and semantic mapping chapters.

>>>>

\section{Summary}
This chapter has introduced concepts used as base during the process of semantic mapping.
For that, it introduced classification tasks in a generic way, it explains the
difference between supervised and unsupervised approaches, how to obtain multi-class
classifiers on top of two class classifications, and how to perform those operations
in implicit spaces by using a kernel function.
It also presented both local and global visual features that are often used in
computer vision for either detecting objects or classifying appearances.
Some probability theory bases were presented together with graphical models that
allow to perform inference on several variables by creating a model of how variables
directly influence each others.

All this concepts were presented and papers and standard text books referenced, 
with the purpose to make the reader familiar with the tools that are used
to extract the higher level features that the semantic mapping process and how does
the process infers semantic labels on the detected areas.

### 2011-07-04 thesis/semantic-mapping.tex
Added summary on end of background and semantic mapping chapters.

>>>>

\section{Summary}
This chapter has introduced the semantic mapping process that is used as base platform
where to perform detection of novel semantic place categories.
It presented the spatial knowledge representation used by it, and shows how the knowledge
is used during the mapping process to identify entities and classify places according
to a set of human defined semantics.
